The \dealii{} Library, Version 8.5

### 2017-03-10 8.5/paper.tex
Abbreviated some points under "major changes"

The major changes of this release are:
\marginpar{Add one sentence to each of the following.}
\begin{itemize}
\item The \texttt{CellDataStorage} class provides a mechanism to store
  user-defined data on each cell. This data is treated as a first-class
  citizen to \dealii{} and, when used in conjunction with other classes,
  can be shipped to other MPI cores during mesh refinement and
  repartitioning.

@@

\item the \texttt{LinearOperator} class has been extended by a generic
  ``payload'' mechanism that allows to attach arbitrary additional
  information to a \texttt{LinearOperator}. The mechanism was used to
  implement a \texttt{TrilinosPayload} class to have full support for using
  the suite of {\trilinos} iterative solvers and preconditioners with a
  \texttt{LinearOperator}.

>>>>

The major changes of this release are:
\marginpar{Add one sentence to each of the following.}
\begin{itemize}
\item The \texttt{CellDataStorage} class provides a safe mechanism to store
  and communicate user-defined data on each cell.

@@

\item The \texttt{LinearOperator} class has been extended by a generic
  ``payload'' mechanism that allows the attachment of arbitrary additional
  information to a \texttt{LinearOperator}.
